Word Sense Disambiguation

### 2011-04-13 paper/paper.Rnw

>>>>

\section{Looking through Different Corpora}

In order to get more data to use with the bootstrapping algorithm, we attempted to search through the Brown corpus and return all of the words that were being disambiguated in the Senseval 3 task.  To do this we needed to find all of the instances of the words that we needed to disambiguate and return a context (list of words) and the position of the word in that list.  We also made sure that we the context that we returned both started at the beginning of the sentence and ended at the end of a sentence and had a minimum of 25 words returned on either side of the word.  This data would then be converted into the form of the data that we received from the Senseval document and ran through the bootstrapping algorithm to have more data to train with.  However when we actually tested this feature alone we found it to be very uninformative.  First, there were very few instances of the words that we were looking for (ex: activate only appeared 3 times), which made searching through the entire corpus to find these words more time consuming than it was helpful.  Therefore, we decided not to use it for the actual test because it was not informative enough by itself.
